---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# denodoExtractor

<!-- badges: start -->
<!-- badges: end -->

The goal of denodoExtractor is to make it  easy to pull common patient flow metrics from denodo views into R. Examples include daily ED visits, admits/census/discharges for specified nursing units, etc. 

## Installation

You can install the package from GitHub: 


```{r install}
# install.packages("devtools")
devtools::install_github("nayefahmad/denodoExtractor")

```



## Example

This is a basic example which shows you how to set up the Denodo ODBC connection and pull admits data. I assume you have set up the Denodo ODBC Driver, and that you have a ODBC connection named "cnx_denodo_spappcsta001". If you have a different name, you can pass that to the `dsn_name` argument of the `setup_denodo()` function.  

First, let's set up our ODBC connection: 

```{r denodo-connex}
library(denodoExtractor)

# first set up odbc: 
setup_denodo()
# should return 3 views: vw_adtc, vw_census, vw_eddata


```

Let's pull admits to major LGH units in January: 

```{r extract-admits}
extract_admits("20190101", "20190201")

```

Now let's try VGH ECC unit instead: 
```{r}
extract_admits("20190101", 
               "20190115",
               site = "Vancouver General Hospital", 
               n_units = "ECC")

```

## Getting help 
To see a list of all available functions, use the following: 

```{r}
# help(package = "denodoExtractor")
```



To see documentation for a specific function, use a question mark followed by the function name in the console. For example: 

```{r}
# ?setup_denodo
# ?extract_admits
```



## Notes on package development 

### Problems with filepaths 
You may run into an error like `UNC paths are not supported. Defaulting to Windows directory`. What seems to work is to go into Tools > Project Options > Build toold > Package directory, and set the folder path *without using paths that start with "vch.ca"*. For example, use `H:/denodoExtractor` 


### Git problems
When using `usethis::use_github`, by default, your .git folder will have a file named `pre-commit` in it. This tells git to do the checks specified there before you can commit anything. Unfortunately, this seems to create problems with using RStudio or GitHub desktop to commit/push. You will have to use git bash with command `git commit --no-verify`. There’s no way to specify this command in GUIs.

To get around this, simply add .sample at the end of the filename: pre-commit.sample. Now it will be ignored by GitHub.

